Mitigating Interest Flooding DDoS Attacks in Named Data Networking

### 2012-12-04 03-interest-flooding.tex
Small corrections
git-svn-id: https://ndnpub.parc.com/ndn-papers/NDN-SEC/dos-protection@853 df1a90cd-247b-4364-bdaf-287a704eb499

%??? - References about other attacks and explicitly stating that this work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles and malicious gateways.

@@

Interest flooding attack belongs to a class of network-level flooding attacks, where an attacker or a set of distributed attackers inject excessive amounts of Interests in order to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
%
% Definition of service
%
Service for legitimate users is disrupted when the network fails to satisfy Interests either because the Interests did not get through to the data producer or nearby cache, or the Data were lost on the way back to the requester (e.g., because of congested links).

@@

\paragraph{Effectiveness}
% Эффективность атаки

To efficiently implement the Interest flooding attack, an adversary needs to make sure that (1) the expressed Interests are getting as close to the Data producer as possible, as well as (2) the corresponding PIT entry (state) is kept on NDN routers for as long as possible.
In order to achieve effectively the first requirement, the malicious Interests should avoid collapsing and cache hits.
To keep PIT entry for a prolonged period of time, the malicious Interests should not bring any data.%
\footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.  For example, and we assume this in the rest of the paper, the maximum time for which any Interest is admitted is one second.}

In other words, to maximize effect of the attack, each malicious Interest generated by individual attack bots should have a unique name and should not correspond to any existing data (\emph{unique junk Interests}).

@@

In this paper we are making the following assumptions about the Interest flooding attack:
\begin{itemize}
\item only client nodes can be compromised and become attack bots;
\item there are no colluding attackers inside the Data producer's network; and
\item the attack is carried only using unique junk Interests.
\end{itemize}

@@

% Though NDN is capable of multipath Interest forwarding and forwarding strategy switching, we are using Best Route (single path) forwarding strategy in all of our experiments.

>>>>

%??? - References to the discussion about other types of attacks (ordifferent attack assumptions) about other attacks and explicitly stating that this work aims to build a baseline for general Interest Flooding mitigation problem, with other attack profiles and malicious gateways.

@@

Interest flooding attack belongs to a class of network-level flooding attacks, where an attacker or a set of distributed attackers inject excessive amounts of Interests in order to overload the network and cause service disruptions for legitimate users (Fig.~\ref{fig:flooding example}).
Service for legitimate users is disrupted when the network fails to satisfy Interests either because the Interests did not get through to the data producer or nearby cache, or the Data were lost on the way back to the requester (e.g., because of congested links).

@@

\paragraph{Effectiveness}

To efficiently implement the Interest flooding attack, an adversary needs to make sure (1) that the expressed Interests are getting as close to the Data producer as possible, and (2) that the corresponding PIT entries (state) are kept on NDN routers for as long as possible.
In order to achieve effectively the first requirement, the malicious Interests should avoid collapsing and cache hits.
To keep PIT entries for a prolonged period of time, the malicious Interests should not bring any data.%
\footnote{While NDN allows users to specify lifetime of the Interest inside the Interest packet~\cite{ndn-conext,ndn-tr}, it is router's decision for how long it is willing to keep the PIT entry.  For example, and we assume this in the rest of the paper, the maximum time for which any Interest is admitted is one second.}

In other words, to maximize effect of the attack, each malicious Interest generated by an individual attack bot should have a unique name and should not correspond to any existing data (\emph{unique junk Interests}).

@@

In this paper we are making the following assumptions about the Interest flooding attack:
\begin{itemize}
\item only client nodes can be compromised and become attack bots;
\item there are no colluding attackers inside the Data producer's network;
\item the attack is carried only using unique junk Interests; and
\item there is only one Data producer for the attacked prefix.
\end{itemize}

@@
